### 2016-03-15 postdoctoral/gamma_functions.tex
some tweaks to gamma functions notes

  \begin{definition}
    A generalized inverse limit \(\varprojlim \{X_p, f_{p,q}, D\}\) is a
    subspace of \(\prod_{p\in D}X_p\) defined for
    a directed set \(\<D,\leq\>\),
    topological spaces \(X_p\) for each \(p\in D\),
    and relations \(f_{p,q}\subseteq X_q\times X_p\) for each
    \(p,q\in D\) where \(p\leq q\). Elements in  \(\varprojlim \{X, f, D\}\)
    are the sequences \(\vect x\) such that \(p\leq q\) implies
    \(\vect x(p)\in f_{p,q}(\vect x(q))\).
  \end{definition}

  \begin{definition}
    An uppersemicontinuous (u.s.c.) relation is a closed subset of the
    square.
  \end{definition}

  \begin{theorem}[summarized in \cite{VARAGONApreprint}]
    If \(L\) is totally ordered, \(X_p\) is a continuum for all \(p\in L\),
    and \(f_{p,q}\) is u.s.c. and continuum-valued for each \(p\leq q\in L\),
    then \(\varprojlim\{X,f,L\}\) is a continuum.
  \end{theorem}

@@

  \begin{definition}
    A V-map \(f\subseteq X^2\) is a continuum-valued u.s.c. idempotent
    surjection.
  \end{definition}

  \begin{definition}
    A u.s.c. map \(f\subseteq X^2\)
    satisfies condition \(\Gamma\) if there exists \(x,y\in X\) such that
    \(\<x,x\>,\<y,y\>,\<x,y\>\in f\).
  \end{definition}

  \begin{theorem}[\cite{CLONTZVARAGONA}]
    Every V-map on a compact connected LOTS satisfies condition \(\Gamma\).
  \end{theorem}

@@

  \begin{definition}
    For any total order \(\<L,\leq\>\), let \(\check L\) be the collection of
    leftward subsets of \(L\)
    (subsets for which \(b\in L,a\leq b\Rightarrow a\in L\))
    linearly ordered by \(\subseteq\), and let \(\hat L\) be the collection
    of left-closed subsets of \(L\) (leftward subsets which are closed)
    linearly ordered by \(\subseteq\).
  \end{definition}

@@

  \begin{proof}
    Each subset \(S\) has an infimum \(\cap S\) and a supremum \(\cup S\)
    (or \(\cl(\cap S)\)).
  \end{proof}

@@

  \begin{definition}
    For any space \(M\) containing the points \(0\) and \(1\),
    let \(\gamma\) be the surjective u.s.c. map on \(K\) where
    \(\gamma(0)=M\) and \(\gamma(t)=\{1\}\)
    for \(t\not=0\).
  \end{definition}

  Note when \(M\) is a Hausdorff continuum, then \(\gamma\) is a V-map.
  It's usually assumed \(0\) is the minimum and \(1\) is the maximum
  when \(M\) is a LOTS.

>>>>

  \begin{definition}
    A generalized inverse limit \(\varprojlim \{X_p, f_{p,q}, D\}\) is a
    subspace of \(\prod_{p\in D}X_p\) defined for
    a directed set \(\<D,\leq\>\),
    topological spaces \(X_p\) for each \(p\in D\),
    and bonding relations \(f_{p,q}\subseteq X_q\times X_p\) for each
    \(p,q\in D\) where \(p\leq q\). Elements in
    \(\varprojlim \{X_p, f_{p,q}, D\}\)
    are the sequences \(\vect x\) such that \(p\leq q\) implies
    \(\vect x(p)\in f_{p,q}(\vect x(q))\).
  \end{definition}

  \begin{definition}
    An left-total relation on \(X\times Y\) satisfies
    \(\forall x\in X\exists y\in Y(\<x,y\>\in f)\).
  \end{definition}

  \begin{definition}
    A left-total relation which is a closed subset of the rectangle
    \(X\times Y\) is called upper-semicontinuous or u.s.c.
    (Equivalently, its corresponding set-valued map \(X\to C(Y)\)
    is continuous.)
  \end{definition}

  \begin{theorem}[summarized in \cite{VARAGONApreprint}]
    If \(L\) is totally ordered, \(X_p\) is a continuum for all \(p\in L\),
    and \(f_{p,q}\) is u.s.c. and continuum-valued for each \(p\leq q\in L\),
    then \(\varprojlim\{X_p,f_{p,q},L\}\) is a continuum.
  \end{theorem}

  \begin{definition}
    An surjective relation on \(X\times Y\) satisfies
    \(\forall y\in Y\exists x\in X(\<x,y\>\in f)\).
  \end{definition}

@@

  \begin{definition}
    A u.s.c. idempotent surjective relation
    \(f\subseteq X^2\) is called a V-relation.
  \end{definition}

  \begin{definition}
    A continuum-valued V-relation is called a CV-relation.
  \end{definition}

  \begin{definition}
    A relation \(f\subseteq X^2\)
    satisfies condition \(\Gamma\) if there exists \(x,y\in X\) such that
    \(\<x,x\>,\<y,y\>,\<x,y\>\in f\).
  \end{definition}

  \begin{theorem}[\cite{CLONTZVARAGONA}]
    Every CV-relation on a compact connected LOTS satisfies condition \(\Gamma\).
  \end{theorem}

@@

  \begin{definition}
    For any total order \(\<L,\leq\>\), let \(\check L\) be the collection of
    leftward subsets of \(L\)
    (subsets for which \(b\in L,a\leq b\Rightarrow a\in L\))
    totally ordered by \(\subseteq\), and let \(\hat L\) be the collection
    of left-closed subsets of \(L\) (leftward subsets which are closed)
    totally ordered by \(\subseteq\).
  \end{definition}

@@

  \begin{proof}
    Each subset \(S\) has an infimum \(\cap S\) and a supremum \(\cup S\)
    (or \(\cl(\cup S)\)).
  \end{proof}

@@

  \begin{definition}
    For any space \(M\) containing the points \(0\) and \(1\),
    let \(\gamma\) be the V-relation on \(K\) where
    \(\gamma(0)=M\) and \(\gamma(t)=\{1\}\)
    for \(t\not=0\).
  \end{definition}

  Note when \(M\) is a Hausdorff continuum, then \(\gamma\) is a CV-relation.
  It's usually assumed \(0\) is the minimum and \(1\) is the maximum
  when \(M\) is a LOTS.
